---
title: "Project 1  Reproducible Researh"
author: "Leonardo Toglia"
date: "14 de noviembre de 2016"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(statsr)
library(Formula)
library(Hmisc)



```

## About the project
It is now possible to collect a large amount of data about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. These type of devices are part of the “quantified self” movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. But these data remain under-utilized both because the raw data are hard to obtain and there is a lack of statistical methods and software for processing and interpreting the data.

This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 minute intervals through out the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day

## Loading the data set 

```{r }
knitr::opts_chunk$set(echo = TRUE)
data<-read.csv("activity.csv")
```


## QUESTION 1: What is mean total number of steps taken per day?

In this plot we calculated the median and mean sums by day.
```{r ,echo=TRUE}
stepsday <- aggregate(steps ~ date, data, sum)
hist(stepsday$steps, main = paste("Total Steps Each Day"), col="red", xlab="# of Steps")
resultmean <- mean(stepsday$steps)
resultmedian <- median(stepsday$steps)

resultmean
resultmedian
```

## Question 2: What is the average daily activity pattern?
In thos code we calculate the average of steps for each interval, next we plot the results and find the maximum.
```{r, echo=TRUE}
interval <- aggregate(steps ~ interval, data, mean)

plot(interval$interval,interval$steps, type="l", xlab="Interval", ylab="# of Steps",main="Average Number of Steps per Day by Interval")

maxinterval <- interval[which.max(interval$steps),1]
maxinterval
```

## Question 3 Impute missing values. Compare imputed to non-imputed data.
Because the dataset we need   impute missing values for completed this requeriments we replace the Na with the average from the category.

```{r}
variables <- names(data) %in% c("data$interval", "data$steps","data$weekdays")
subdata2 <- data[variables]
subdata2 <-na.delete(subdata2)
```

This date is the firt with 9000 steps or more 
```{r,echo=TRUE}
subdata2[as.character(subdata2$date) == "2012-10-01", 1] <- 0
```

Now we recalculated the median and mean 


```{r}
# Compute the total number of steps each day (NA values removed)
sumdata <- aggregate(data$steps, by=list(data$date), FUN=sum)

# Rename the attributes
names(sumdata) <- c("date", "total")

# Compute the histogram of the total number of steps each day
hist(sumdata$total, 
     breaks=seq(from=0, to=25000, by=2500),
     col="blue", 
     xlab="Total number of steps", 
     ylim=c(0, 30), 
     main="Histogram of the total number of steps taken each day\n(NA replaced by mean value)")
```


```

```

